---
title: "Counterparty Credit Risk and CVA Modelling"
author: "Gautam"
date: "2026-05-24"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.align = "center", fig.width = 9, fig.height = 5)
```

# Introduction

This project calculates the unilateral Credit Valuation Adjustment (CVA) for a derivatives portfolio against Deutsche Bank, made up of:

-   a 3-year EUR/PLN FX Forward, notional 1,000,000 EUR, strike 4.4439, and
-   a 3-year EUR receiver Interest Rate Swap on EURIBOR 3M, notional 10,000,000 EUR, fixed rate 2.02 percent.

CVA formula:

$$
CVA \;=\; (1-R) \sum_{i=1}^{N} EE(t_i) \cdot DF(0,t_i) \cdot q(t_{i-1}, t_i)
$$

# Setup

```{r libs}
# install.packages(c("readxl","dplyr"))
library(readxl); library(dplyr)
options(scipen = 999)
```

# Market Data

```{r read-data}
raw_data <- read_excel(
  "/Users/gautamprasad/Desktop/masters/sem 4/Quantitative finance - project/5/finalforme.xlsx",
  sheet = "Market data"
)
```

## Market reference data

```{r market-data}
market_data <- raw_data %>%
  select(Month, EUR_Rate, PLN_rate, EUR_DF, PLN_DF, `EUR/PLN`) %>% na.omit()
saveRDS(market_data, "market_data.rds")
head(market_data)
```

## FX historical series

```{r fx-data}
fx_data <- raw_data %>% select(Date_fx, Close) %>% na.omit()
fx_data$Close     <- as.numeric(fx_data$Close)
fx_data$fx_return <- c(NA, diff(fx_data$Close) / fx_data$Close[-length(fx_data$Close)])
fx_data <- na.omit(fx_data)
saveRDS(fx_data, "fx_data.rds")
head(fx_data)
```

## IRS historical series

```{r irs-data}
irs_data <- raw_data %>% select(Date_irs, irs_eurobor3m) %>% na.omit()
irs_data$irs_eurobor3m <- as.numeric(irs_data$irs_eurobor3m)
irs_data$irs_change    <- c(NA, diff(irs_data$irs_eurobor3m) / 100)
irs_data <- na.omit(irs_data)
saveRDS(irs_data, "irs_data.rds")
head(irs_data)
```

## Correlation between FX returns and IRS changes

```{r correlation}
correlation_data <- merge(
  fx_data[, c("Date_fx", "fx_return")],
  irs_data[, c("Date_irs", "irs_change")],
  by.x = "Date_fx", by.y = "Date_irs", all = FALSE
)
colnames(correlation_data) <- c("Date", "FX_Return", "IRS_Change")
saveRDS(correlation_data, "correlation_data.rds")
cat("Historical FX vs IRS correlation:",
    round(cor(correlation_data$FX_Return, correlation_data$IRS_Change), 4), "\n")
```

```{r load-rds}
market_data      <- readRDS("market_data.rds")
fx_data          <- readRDS("fx_data.rds")
irs_data         <- readRDS("irs_data.rds")
correlation_data <- readRDS("correlation_data.rds")
```

# Model Parameters

```{r params}
T_h   <- 3
steps <- 36
dt    <- 1/12
n_sim <- 10000

r_pln <- 0.0375
r_eur <- 0.0200

N_fx  <- 1000000
N_irs <- 10000000
K_fx  <- 4.4439
fixed_rate <- 0.0202

s0_fx           <- tail(fx_data$Close, 1)
sigma_fx_daily  <- sd(fx_data$fx_return)
sigma_fx_annual <- sigma_fx_daily * sqrt(252)
mu_fx           <- r_pln - r_eur

r0_ir           <- tail(irs_data$irs_eurobor3m, 1) / 100
sigma_ir_daily  <- sd(irs_data$irs_change)
sigma_ir_annual <- sigma_ir_daily * sqrt(252)
mu_ir           <- mean(as.numeric(irs_data$irs_change))

time_grid <- seq(0, T_h, by = dt)
df_eur    <- exp(-r_eur * time_grid)
df_pln    <- exp(-r_pln * time_grid)
```

# FX Forward Model

GBM dynamics:

$$
S_{t+1} \;=\; S_t \exp \!\left[ \left(\mu - \tfrac12 \sigma^2 \right) \Delta t + \sigma \sqrt{\Delta t}\, Z \right]
$$

```{r fx-sim}
set.seed(123)
fx_paths <- matrix(0, nrow = steps + 1, ncol = n_sim)
fx_paths[1, ] <- s0_fx
for(i in 2:(steps + 1)) {
  z <- rnorm(n_sim)
  fx_paths[i, ] <- fx_paths[i - 1, ] *
    exp((mu_fx - 0.5 * sigma_fx_annual^2) * dt +
         sigma_fx_annual * sqrt(dt) * z)
}
```

FX Forward valuation (Garman-Kohlhagen):

$$
V_{FX}(t) \;=\; N_{fx} \left[ S(t) \, e^{-r_{EUR}\,\tau} - K \, e^{-r_{PLN}\,\tau} \right], \quad \tau = T - t
$$

```{r fx-valuation}
fx_mtm <- matrix(0, nrow = steps + 1, ncol = n_sim)
for(i in 1:(steps + 1)) {
  tau <- T_h - time_grid[i]
  fx_mtm[i, ] <- N_fx * (
    fx_paths[i, ] * exp(-r_eur * tau) -
    K_fx          * exp(-r_pln * tau)
  )
}
fx_EE <- rowMeans(pmax(fx_mtm, 0))
```

# Interest Rate Swap Model

ABM dynamics:

$$
r_{t+1} \;=\; r_t + \mu \Delta t + \sigma \sqrt{\Delta t}\, Z
$$

```{r ir-sim}
ir_paths <- matrix(0, nrow = steps + 1, ncol = n_sim)
ir_paths[1, ] <- r0_ir
for(i in 2:(steps + 1)) {
  z <- rnorm(n_sim)
  ir_paths[i, ] <- ir_paths[i - 1, ] +
                   mu_ir * dt +
                   sigma_ir_annual * sqrt(dt) * z
}
```

IRS valuation in EUR (receiver, set-in-advance, deterministic EUR discounting):

$$
V_{IRS}(t) \;=\; \sum_{T_k > t} \big[\,\text{Fixed}(T_k) - \text{Floating}(T_k)\,\big] \cdot \frac{P_{EUR}(0,T_k)}{P_{EUR}(0,t)}
$$

```{r irs-valuation}
irs_mtm <- matrix(0, nrow = steps + 1, ncol = n_sim)
for(i in 1:(steps + 1)) {
  for(j in 1:n_sim) {
    value <- 0
    if(i < steps + 1) {
      for(k in (i + 1):(steps + 1)) {
        month <- k - 1
        floating_leg <- 0
        if(month %% 3 == 0 && month > 0) {
          reset_idx <- k - 3
          if(reset_idx >= 1) floating_leg <- N_irs * ir_paths[reset_idx, j] * 0.25
        }
        fixed_leg <- 0
        if(month %% 12 == 0 && month > 0) fixed_leg <- N_irs * fixed_rate
        cashflow <- fixed_leg - floating_leg
        df_fwd   <- df_eur[k] / df_eur[i]
        value    <- value + cashflow * df_fwd
      }
    }
    irs_mtm[i, j] <- value
  }
}
irs_EE <- rowMeans(pmax(irs_mtm, 0))
```

IRS in PLN (deterministic forward FX):

```{r irs-pln}
fx_forward_curve <- market_data$`EUR/PLN`
irs_mtm_pln <- matrix(0, nrow = steps + 1, ncol = n_sim)
for(i in 1:(steps + 1)) {
  irs_mtm_pln[i, ] <- irs_mtm[i, ] * fx_forward_curve[i]
}
irs_EE_pln <- rowMeans(pmax(irs_mtm_pln, 0))
```

# Portfolio Exposure

$$
EE_{port}(t) \;=\; \mathbb{E} \Big[ \max\!\big( MtM_{FX}(t) + MtM_{IRS\,PLN}(t),\; 0 \big) \Big]
$$

```{r portfolio}
portfolio_mtm <- fx_mtm + irs_mtm_pln
portfolio_EE  <- rowMeans(pmax(portfolio_mtm, 0))
```

# Variation Margin

$$
VM(T) \;=\; MtM_{FX}(T-1) + MtM_{IRS\,PLN}(T-1), \qquad VM(0) = 0
$$

$$
\text{Exposure}_{VM}(T) \;=\; \max\!\big( MtM_{port}(T) - VM(T),\; 0 \big)
$$

```{r vm}
vm <- matrix(0, nrow = steps + 1, ncol = n_sim)
vm[1, ] <- 0
for(i in 2:(steps + 1)) vm[i, ] <- fx_mtm[i - 1, ] + irs_mtm_pln[i - 1, ]
vm_exposure <- pmax(portfolio_mtm - vm, 0)
vm_EE       <- rowMeans(vm_exposure)
```

# CDS Bootstrap

$$
S \cdot \sum_{n=1}^{N} DF(0,T_n) \, PS(T_n) \, \Delta t_n
\;=\;
(1-R) \cdot \sum_{n=1}^{N} DF(0,T_n) \, [\,PS(T_{n-1}) - PS(T_n)\,]
$$

```{r cds-bootstrap}
cdsTenors  <- c(0.5, 1, 2, 3)
cdsSpreads <- c(0.00305, 0.00394, 0.006935, 0.00967)
DF         <- exp(-r_eur * cdsTenors)
RR <- 0.40; LGD <- 1 - RR

PS <- numeric(length(cdsTenors))
solve_PS <- function(k, PS_prev) {
  S <- cdsSpreads[k]
  f <- function(PS_k) {
    PS_full <- c(1, PS_prev, PS_k); PL <- 0; DL <- 0
    for(i in 2:(k + 1)) {
      t_now  <- cdsTenors[i - 1]
      t_prev <- ifelse(i == 2, 0, cdsTenors[i - 2])
      dt_cds <- t_now - t_prev
      DL <- DL + LGD * DF[i - 1] * (PS_full[i - 1] - PS_full[i])
      PL <- PL + S   * DF[i - 1] *  PS_full[i]    * dt_cds
    }
    PL - DL
  }
  uniroot(f, c(0.5, 1))$root
}
PS[1] <- LGD / (LGD + cdsSpreads[1] * cdsTenors[1])
for(k in 2:length(cdsTenors)) PS[k] <- solve_PS(k, PS[1:(k - 1)])

t_monthly    <- seq(0, 3, by = 1/12)
PS_interp    <- approx(c(0, cdsTenors), c(1, PS), xout = t_monthly)$y
default_prob <- c(0, PS_interp[-length(PS_interp)] - PS_interp[-1])

data.frame(Tenor = cdsTenors, Survival = round(PS, 6))
```

# CVA Calculation

$$
CVA \;=\; (1-R) \sum_{i=1}^{N} EE(t_i) \cdot P_{PLN}(0,t_i) \cdot q(t_{i-1}, t_i)
$$

```{r cva}
discount_factors <- market_data$PLN_DF[1:37]

CVA_FX        <- LGD * sum(fx_EE        * discount_factors * default_prob)
CVA_IRS_PLN   <- LGD * sum(irs_EE_pln   * discount_factors * default_prob)
CVA_PORTFOLIO <- LGD * sum(portfolio_EE * discount_factors * default_prob)
CVA_VM        <- LGD * sum(vm_EE        * discount_factors * default_prob)

cva_results <- data.frame(
  Instrument = c("FX Forward", "IRS (PLN)", "Portfolio", "Portfolio with VM"),
  CVA_PLN    = round(c(CVA_FX, CVA_IRS_PLN, CVA_PORTFOLIO, CVA_VM), 2)
)
print(cva_results)

netting_benefit <- 1 - CVA_PORTFOLIO / (CVA_FX + CVA_IRS_PLN)
vm_efficiency   <- 1 - CVA_VM / CVA_PORTFOLIO
cat("\nNetting benefit:", round(netting_benefit * 100, 2), "%\n")
cat("VM efficiency  :", round(vm_efficiency  * 100, 2), "%\n")
```

# Graphs

```{r graph-globals}
months <- 0:steps
n_show <- 50
```

## Simulated FX paths

```{r g1-fx-paths, fig.height=5}
par(mar = c(4.5, 4.8, 3.5, 1.5))
matplot(months, fx_paths[, 1:n_show], type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "EUR/PLN spot rate",
        main = "Simulated EUR/PLN exchange rate paths (50 of 10,000)")
lines(months, rowMeans(fx_paths), col = "black", lwd = 3)
abline(h = K_fx, col = "red", lty = 2, lwd = 1.8)
legend("topleft",
       legend = c("Sample paths", "Mean path", paste("Strike =", K_fx)),
       col = c("dodgerblue", "black", "red"), lty = c(1, 1, 2),
       lwd = c(1.5, 3, 1.8), bg = "white", cex = 0.85)
grid(col = "gray90")
```

## FX Forward MtM paths + mean

```{r g2-fx-mtm, fig.height=5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
matplot(months, fx_mtm[, 1:n_show], type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "FX Forward MtM (PLN)",
        main = "FX Forward — simulated MtM paths (50 of 10,000)")
lines(months, rowMeans(fx_mtm), col = "black", lwd = 3)
abline(h = 0, col = "gray40", lty = 2)
legend("topleft", legend = c("Sample paths", "Mean MtM"),
       col = c("dodgerblue", "black"), lty = 1, lwd = c(1.5, 3),
       bg = "white", cex = 0.85)
grid(col = "gray90")
```

## FX Expected Exposure

```{r g3-fx-ee, fig.height=4.5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
plot(months, fx_EE, type = "n",
     xlab = "Month", ylab = "Expected Exposure (PLN)",
     main = "FX Forward — Expected Exposure")
polygon(c(0, months, steps), c(0, fx_EE, 0),
        col = adjustcolor("steelblue", 0.25), border = NA)
lines(months, fx_EE, col = "steelblue4", lwd = 2.5)
points(months, fx_EE, col = "black", pch = 19, cex = 0.9)
grid(col = "gray90")
```

## Simulated EURIBOR 3M paths

```{r g4-ir-paths, fig.height=5}
par(mar = c(4.5, 4.8, 3.5, 1.5))
matplot(months, ir_paths[, 1:n_show] * 100, type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "EURIBOR 3M (%)",
        main = "Simulated EURIBOR 3M paths (50 of 10,000)")
lines(months, rowMeans(ir_paths) * 100, col = "black", lwd = 3)
abline(h = fixed_rate * 100, col = "red", lty = 2, lwd = 1.8)
legend("topleft",
       legend = c("Sample paths", "Mean rate",
                  paste0("Fixed = ", fixed_rate * 100, "%")),
       col = c("darkcyan", "black", "red"), lty = c(1, 1, 2),
       lwd = c(1.5, 3, 1.8), bg = "white", cex = 0.85)
grid(col = "gray90")
```

## IRS MtM paths (EUR)

```{r g5-irs-eur, fig.height=5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
matplot(months, irs_mtm[, 1:n_show], type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "IRS MtM (EUR)",
        main = "IRS — simulated MtM paths in EUR (50 of 10,000)")
lines(months, rowMeans(irs_mtm), col = "black", lwd = 3)
abline(h = 0, col = "gray40", lty = 2)
legend("topright", legend = c("Sample paths", "Mean MtM"),
       col = c("forestgreen", "black"), lty = 1, lwd = c(1.5, 3),
       bg = "white", cex = 0.85)
grid(col = "gray90")
```

## IRS MtM paths (PLN)

```{r g6-irs-pln, fig.height=5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
matplot(months, irs_mtm_pln[, 1:n_show], type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "IRS MtM (PLN)",
        main = "IRS — simulated MtM paths in PLN (50 of 10,000)")
lines(months, rowMeans(irs_mtm_pln), col = "black", lwd = 3)
abline(h = 0, col = "gray40", lty = 2)
legend("topright", legend = c("Sample paths", "Mean MtM"),
       col = c("forestgreen", "black"), lty = 1, lwd = c(1.5, 3),
       bg = "white", cex = 0.85)
grid(col = "gray90")
```

## IRS Expected Exposure (PLN)

```{r g7-irs-ee, fig.height=4.5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
plot(months, irs_EE_pln, type = "n",
     xlab = "Month", ylab = "Expected Exposure (PLN)",
     main = "IRS — Expected Exposure in PLN")
polygon(c(0, months, steps), c(0, irs_EE_pln, 0),
        col = adjustcolor("forestgreen", 0.25), border = NA)
lines(months, irs_EE_pln, col = "darkgreen", lwd = 2.5)
points(months, irs_EE_pln, col = "black", pch = 19, cex = 0.9)
grid(col = "gray90")
```

## Portfolio MtM paths

```{r g8-port-paths, fig.height=5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
matplot(months, portfolio_mtm[, 1:n_show], type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "Portfolio MtM (PLN)",
        main = "Portfolio — simulated MtM paths (50 of 10,000)")
lines(months, rowMeans(portfolio_mtm), col = "black", lwd = 3)
abline(h = 0, col = "gray40", lty = 2)
legend("topright", legend = c("Sample paths", "Mean MtM"),
       col = c("purple4", "black"), lty = 1, lwd = c(1.5, 3),
       bg = "white", cex = 0.85)
grid(col = "gray90")
```

## Portfolio Expected Exposure

```{r g9-port-ee, fig.height=4.5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
plot(months, portfolio_EE, type = "n",
     xlab = "Month", ylab = "Expected Exposure (PLN)",
     main = "Portfolio — Expected Exposure")
polygon(c(0, months, steps), c(0, portfolio_EE, 0),
        col = adjustcolor("purple4", 0.25), border = NA)
lines(months, portfolio_EE, col = "purple4", lwd = 2.5)
points(months, portfolio_EE, col = "black", pch = 19, cex = 0.9)
grid(col = "gray90")
```

## VM residual exposure paths

```{r g10-vm-paths, fig.height=5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
matplot(months, vm_exposure[, 1:n_show], type = "l", lty = 1, lwd = 0.8,
        col = rainbow(n_show, s = 0.85, v = 0.85, alpha = 0.55),
        xlab = "Month", ylab = "Residual exposure (PLN)",
        main = "Portfolio after monthly VM — residual exposure (50 of 10,000)")
lines(months, vm_EE, col = "black", lwd = 3)
legend("topright", legend = c("Sample paths", "Mean residual"),
       col = c("firebrick", "black"), lty = 1, lwd = c(1.5, 3),
       bg = "white", cex = 0.85)
grid(col = "gray90")
```

## Portfolio EE: without vs with VM

```{r g11-vs-vm, fig.height=4.5}
par(mar = c(4.5, 5.8, 3.5, 1.5))
plot(months, portfolio_EE, type = "l", lwd = 2.5, col = "green",
     xlab = "Month", ylab = "Expected Exposure (PLN)",
     main = "Portfolio EE — without vs with monthly VM",
     ylim = c(0, max(portfolio_EE) * 1.05))
lines(months, vm_EE, col = "black", lwd = 2.5, lty = 2)
legend("topright", legend = c("Without VM", "With monthly VM"),
       col = c("green", "black"), lty = c(1, 2), lwd = 2.5,
       bg = "white", cex = 0.85)
grid(col = "gray90")
```

## CDS survival and default probability

```{r g12-cds, fig.width=10, fig.height=4.5}
par(mfrow = c(1, 2), mar = c(4.5, 4.8, 3.5, 1.5))

plot(t_monthly, PS_interp, type = "l", lwd = 2.5, col = "steelblue",
     xlab = "Time (years)", ylab = "Survival PS(t)",
     main = "CDS-implied survival probability")
points(cdsTenors, PS, col = "red", pch = 19, cex = 1.3)
grid(col = "gray90")

plot(t_monthly, default_prob, type = "l", lwd = 2.5, col = "firebrick",
     xlab = "Time (years)", ylab = "Marginal default q(t)",
     main = "Monthly marginal default probability")
grid(col = "gray90")

par(mfrow = c(1, 1))
```

## CVA summary bar chart

```{r g13-cva-bar, fig.height=5}
par(mar = c(5, 5.5, 4, 1.5))
cols <- c("steelblue", "forestgreen", "purple4", "firebrick")
ymax <- max(cva_results$CVA_PLN) * 1.20

bp <- barplot(cva_results$CVA_PLN,
              names.arg = cva_results$Instrument,
              col = cols, border = "white", space = 0.55,
              ylim = c(0, ymax),
              xlab = "", ylab = "CVA (PLN)",
              main = "CVA Comparison — All Four Instruments")

text(bp, cva_results$CVA_PLN,
     labels = format(round(cva_results$CVA_PLN, 0), big.mark = ","),
     pos = 3, font = 2, cex = 1.05)

mtext(sprintf("Netting benefit: %.1f%%   |   VM efficiency: %.1f%%",
              netting_benefit * 100, vm_efficiency * 100),
      side = 3, line = 0.3, cex = 0.95, col = "gray30")
grid(nx = NA, ny = NULL, col = "gray90")
```

## Cumulative CVA accrual

```{r g14-cum-cva, fig.height=4.5}
monthly_contrib <- portfolio_EE * discount_factors * default_prob * LGD
cum_cva <- cumsum(monthly_contrib)

par(mar = c(4.5, 5.8, 3.5, 1.5))
plot(months, cum_cva, type = "n",
     xlab = "Month", ylab = "Cumulative CVA (PLN)",
     main = paste0("Cumulative CVA accrual — Portfolio (total = ",
                   format(round(CVA_PORTFOLIO, 0), big.mark = ","), " PLN)"))
polygon(c(0, months, steps), c(0, cum_cva, 0),
        col = adjustcolor("steelblue", 0.30), border = NA)
lines(months, cum_cva, col = "steelblue4", lwd = 2.5)
grid(col = "gray90")
```

### Historical risk factors used for calibration

Visual sanity check on the inputs — confirms that the historical EUR/PLN and EURIBOR 3M data used to calibrate σ are in a reasonable range and free of obvious data errors.

```{r g18-hist-data, fig.width=10, fig.height=4.5}
par(mfrow = c(1, 2), mar = c(4.5, 4.8, 3.5, 1.5))

plot(fx_data$Date_fx, fx_data$Close, type = "l", lwd = 1.5, col = "steelblue",
     xlab = "Date", ylab = "EUR/PLN spot",
     main = "Historical EUR/PLN (2023–2025)")
grid(col = "gray90")

plot(irs_data$Date_irs, irs_data$irs_eurobor3m, type = "l", lwd = 1.5,
     col = "forestgreen",
     xlab = "Date", ylab = "EURIBOR 3M (%)",
     main = "Historical EURIBOR 3M (2023–2025)")
grid(col = "gray90")

par(mfrow = c(1, 1))
```

# Conclusions

-   Single-instrument CVAs show the IRS dominating the credit charge because of its 10x larger notional.
-   Netting reduces the standalone-sum CVA by about `r round(netting_benefit * 100, 1)` percent.
-   Monthly Variation Margin further reduces the residual portfolio CVA by about `r round(vm_efficiency * 100, 1)` percent, leaving only the one-period gap-risk component (`r format(round(CVA_VM, 0), big.mark = ",")` PLN).
-   Residual scales with the square root of the margin period, so shorter margin periods shrink CVA further.

# References

-   Brigo, D., Morini, M., Pallavicini, A. (2013). Counterparty Credit Risk, Collateral and Funding. Wiley.
-   Gregory, J. (2020). The xVA Challenge (4th ed.). Wiley.
-   ECB Statistical Data Warehouse. EURIBOR 3M monthly historical series.
-   Stooq.pl. EUR/PLN daily exchange rates.
-   Olsza, P. (2026). Credit Valuation Adjustment for Derivative Contracts — Lecture notes.
